---
title: "Respirometry Trails and Slope Creation for Summer Krill 2019"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: journal
    highlight: zenburn
    smart: false

---


Hello World

Author: OA Lab, NWFSC
Title: Respirometry Trails for Summer Krill 2019
Date: November 2020

#Respirometry Trails and Slope Creation for Summer Krill 2019
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```



```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(purrr)
library(wql)
library(lubridate)
library(arsenal)
library(compareDF)
#for graphing
library(ggplot2)
library(stringr)
library(nlme)
library(RColorBrewer)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```


 
# 1.) Setting Working Directory
```{r 1.) Setting Working Directory }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES")
```



# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe }

#*********************************
## 2.) Creating the intial Dataframe, dtotal
#*********************************


#get all the files in the defined working directory that are in csv format  
dRESP <- read.csv(file = "KRILL_Resp_alltrials.csv", stringsAsFactors = FALSE)
dim(dRESP)

write.csv(dRESP, file = "2020.11.30_presenseSENSORONLY.alltrials.data.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# dRESPanimal represents just the animal, vial, MOATs, etc.  
dRESPanimal <- read.csv(file = "RespirometryTrials_all.Animal.Info.csv") 
dim(dRESPanimal)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# #dRESPmsr represents the measurements made by the presense optical device for Dissolved Oxygen 
# dRESPmsr <- merge(dRESP, dRESPanimal, by="SensorName")

##PRESENSE observations grouped by Krill ID
#dtotal <- read.csv(file = "2020.11.17_dtotal.csv", stringsAsFactors = FALSE)
dRESPmsr <- read.csv(file = "2020.11.18_respirometrymeasurements.csv", stringsAsFactors = FALSE)

dim(dRESPmsr)


unique(dRESPmsr$KrillID)

unique(dRESPmsr$SensorName)
UniqueSensorNames <- levels(dRESPmsr$SensorName)
UniqueSensorNames
# kable(UniqueSensorNames)



```


# 3.) Analysis, Respirometry - Creating the Slope Function 
```{r 3.) Analysis, Respirometry - Creating the Slope Function}
#*********************************
## 3.) Analysis, Respirometry - Creating the Slope Function  
#*********************************  

vialVol <- 28.06 #ml

oxygen <- vialVol * dRESPmsr$actualDOmg   

dRESPmsr$oxygen <- oxygen

#nmol/vial; conversion for L to ml and umol to nmol cancels


#slope funcion of 2 vectors
slope <- function(y,x){
  return(lm(y~x, na.action = na.omit)$coefficients[2])
}
  

dRESPmsr$delta_t <- as.numeric(dRESPmsr$delta_t)

cSlopes <- by(dRESPmsr, dRESPmsr$KrillID, function(x){ slope(x$oxygen, x$delta_t)})


#creating a data frame instead of a list 
ds <- as.data.frame(sapply(cSlopes, I))
#having row names be a variable in a column to be able to pull it out for later merging 
ds$TrialID<- row.names(ds)



```


# 4.) Merging ds and dRESPmsr 
```{r}
#add column to dslopes thats KrillID
#View(dref)
ds$KrillID <- row.names(ds)
#View(dslopes)
dtotal <- merge(dRESPmsr, ds, by = "KrillID")
#View(dtotal)
```


# 5.) Krill ID as a factor & Grouping by Krill ID
```{r}
dtotal$KrillID <- factor(dtotal$KrillID)
nlevels(dtotal$KrillID)


#how best to run the lmlist over
# group and then run a function tidyverse
# group by krill ID and then run the function

# levels(dtotal$KrillID)
# GRP_dtotal <- dtotal %>% group_by(KrillID)
# dtotal <- GRP_dtotal
```



# 6.) Creating Slope Functions & Linear Models 
```{r 6.) Creating Slope Functions & Linear Models }
#*********************************
## 6.) Creating the ds dataframe
#*********************************
# #get slopes and r^2 values from dtotal 

dSlopes <- data.frame(KrillID = levels(dtotal$KrillID))
# dSlopes$slope <- NA
# dSlopes$rsq <- NA

for(i in 1:length(dSlopes$KrillID)){
   m <- lm(oxygen ~ delta_t,
                         dtotal[dtotal$KrillID == dSlopes$KrillID[i],],
                         na.action=na.omit)
  dSlopes$slope[i] <- m$coefficients[2]
  dSlopes$rsq[i] <- summary(m)$r.squared
}

# how to extract p value ... likely pulling it from the summary that the slope is greater than zero
# how likely if the krill held their breath for 2 hours....
# can't use the trial if krill went free diving in the vial


# slopes <- coef(info)[2]
# #print(slopes)
# dslopes <- data.matrix(slopes)
# #View(dref)
# mode(dslopes[,1])
# dslopes <- as.data.frame(dslopes)
# dslopes$slope <- dslopes$delta_t
# dslopes$delta_t <- NULL
# #View(dslopes)

#now for R^2!!

# Rsq <- sapply(dSlopes,function(x) summary(x)[[r.squared]])
# t(Rsq) #transposes rows and columns
# Rsq <- data.matrix(Rsq)
# #View(Rsq)
# KrillSlopes <- cbind(dSlopes, Rsq)
# View(KrilSlopes)

krillslopes <- merge(dtotal, dSlopes, by="KrillID")

dSlopes$SensorName <- ""

dSlopes <- dSlopes %>% group_by(KrillID)
dRESPanimal <- dRESPanimal %>% group_by(SensorName)

dSlopes$KrillID <- as.character(dSlopes$KrillID)
dSlopes$SensorName <- dRESPanimal$SensorName
dSlopes$TrialID <- dRESPanimal$TrialID
dSlopes$MOATS <- dRESPanimal$MOATS
dSlopes$Treatment<- dRESPanimal$Treatment
dSlopes$LoadingLocation<- dRESPanimal$LoadingLocation
dSlopes$VialNum<- dRESPanimal$GlassVialNumber
dSlopes$TelsonLength<- dRESPanimal$TelsonLength..mm.
dSlopes$WetWeight<- dRESPanimal$Size



```



```{r 7.) Analysis, Respirometry - Correcting the Slope for Blanks}

#*********************************
## 7.) Analysis, Respirometry - Correcting the Slope for Blanks 
#*********************************

#blank corrected slope and blank-size corrected slope
## need to correct all slopes with the blanks' slope
## this is the background respiration of whatever phtyos and instrument drift

## create a mean blank slope per trial
## merge with the master(krill slopes) and "correct" all slopes against mean value (per trial)

## maybe an overall blank slope average
# x is equal to the blank vials  


x <- subset(dSlopes, dSlopes$MOATS == "blank")

xtrial1 <- subset(x, x$TrialID == "Trial01")
xtrial2 <- subset(x, x$TrialID == "Trial02")
xtrial3 <- subset(x, x$TrialID == "Trial03")
xtrial4 <- subset(x, x$TrialID == "Trial04")

blankmeanslope1 <- mean(xtrial1$slope)
blankmeanslope2 <- mean(xtrial2$slope)
blankmeanslope3 <- mean(xtrial3$slope)
blankmeanslope4 <- mean(xtrial4$slope)

# #2014 Paul comments/Direction 
# print(blankmeanslope)
# is.numeric(blankmeanslope)
# #now we have a mean of the blanks in each separate trial!
# #View(blankmeanslope)
# as.data.frame(blankmeanslope)
# #add a row that is the trial ID
# blankmeanslope <- cbind(blankmeanslope, levels(dtotal$TrialID))
# #View(blankmeanslope) #good so far!! 20 july
# blankmeanslope[,1] <- as.numeric(blankmeanslope[,1]) #make sure it stays numeric

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#  # # T/S this section ... I don't think we need this anymore

# # alread have trial ID 
# #rename column 2 as TrialID so it matches up with the column in dtotal2
# colnames(blankmeanslope)[2] <- "TrialID"
# #View(blankmeanslope)
# dtotalslope <- merge(dtotal2, blankmeanslope, by="TrialID")
# #View(dtotal3) #all still good 20 july
# dtotal3$blankmeanslope <- as.numeric(as.character(dtotal3$blankmeanslope))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#  # # T/S this section ... I don't think we need this anymore
# # still working off dtotal 3
# dtotal3$slope <- as.numeric(dtotal3$slope)
# 
# #20 july: the blanks themselves are an issue because they're getting the average of themselves and the other blanks taken away from them. what do? 
# dtotal3$blankcorrslope <- (dtotal3$slope - dtotal3$blankmeanslope)
# #View(dtotal3)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



####blank and size corrected slope


dSlopes$CorrSlope <- ""
# animalslopes <- subset(dSlopes, Treatment != "n/a")
# trial01animalslopes <- subset(animalslopes, TrialID == "Trial01")
# trial02animalslopes <- subset(animalslopes, TrialID == "Trial02")
# trial03animalslopes <- subset(animalslopes, TrialID == "Trial03")
# trial04animalslopes <- subset(animalslopes, TrialID == "Trial04")


dSlopes$CorrSlope <- as.numeric(dSlopes$CorrSlope)
dSlopes$slope <- as.numeric(dSlopes$slope)

dSlopes$CorrSlope <- ((subset(dSlopes$slope, dSlopes$TrialID == "Trial01"& dSlopes$MOATS != "blank"))/blankmeanslope1) |
((subset(dSlopes$slope, dSlopes$TrialID == "Trial02" & dSlopes$MOATS != "blank"))/blankmeanslope2) |
((subset(dSlopes$slope, dSlopes$TrialID == "Trial03" & dSlopes$MOATS != "blank"))/blankmeanslope3) | 
((subset(dSlopes$slope, dSlopes$TrialID == "Trial04" & dSlopes$MOATS != "blank"))/blankmeanslope4) 



Trial01corslope <- subset(dSlopes$slope, dSlopes$TrialID == "Trial01"& dSlopes$MOATS != "blank")/blankmeanslope1 

Trial02corslope <- subset(dSlopes$slope, dSlopes$TrialID == "Trial02"& dSlopes$MOATS != "blank")/blankmeanslope2 

Trial03corslope <- subset(dSlopes$slope, dSlopes$TrialID == "Trial02"& dSlopes$MOATS != "blank")/blankmeanslope3

Trial04corslope <- subset(dSlopes$slope, dSlopes$TrialID == "Trial02"& dSlopes$MOATS != "blank")/blankmeanslope4


dSlopes$CorrSlope <- trial01corslope case_when(dSlopes$TrialID == "Trial01"& dSlopes$MOATS != "blank")

dSlopes <- dSlopes %>% mutate(CorrSlope=case_when((dSlopes$TrialID == "Trial01") & (dSlopes$MOATS != "blank")))



dtotal3$blanksizecorrslope <- dtotal3$blankcorrslope/dtotal3$Size
#View(dtotal3)
mode(dtotal3$blanksizecorrslope)
#y <- subset(dtotal3, dtotal3$blanksizecorrslope != "lnf")
#View(y)#dealing with the blank vials' size being zero
#View(dtotal3)
View(dtotal3)
## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   groupvars: a vector containing names of columns that contain grouping variables
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                      conf.interval=.95, .drop=TRUE) {
  library(plyr)
  
  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function (x, na.rm=FALSE) {
    if (na.rm) sum(!is.na(x))
    else       length(x)
  }
  
  # This does the summary. For each group's data frame, return a vector with
  # N, mean, and sd
  datac <- ddply(data, groupvars, .drop=.drop,
                 .fun = function(xx, col) {
                   c(N    = length2(xx[[col]], na.rm=na.rm),
                     mean = mean   (xx[[col]], na.rm=na.rm),
                     sd   = sd     (xx[[col]], na.rm=na.rm)
                   )
                 },
                 measurevar
  )
  
  # Rename the "mean" column    
  datac <- rename(datac, c("mean" = measurevar))
  
  datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
  
  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval: 
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval/2 + .5, datac$N-1)
  datac$ci <- datac$se * ciMult
  
  return(datac)
} 


```




```{r}

#*********************************
## 5.) Analysis, Respirometry - Saturation Calculations  
#*********************************
#saturation calculations!!!

#add columns for temp in kelvin, add temps and salinity to dtotal version 5 #added 7/14: dont i want saturation in mastersheetr? why am i making dtotal5 so long when i could just keep mastersheetr the long one?


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



MasterSheetR$TempK <- MasterSheetR$Temp + 273.15
#temps <- subset(MasterSheetR, select = c(KrillID, Temp, TempK, Salinity))
#dtotal5 <- merge(temps, dtotal4, by="KrillID")
#dtotal5$MeasurementID <- 1:nrow(dtotal5)
#View(MasterSheetR)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



#calculate 100% saturation (mg/L)
saturationfun <- function(Temp, Salinity, Pressure){
  #Temp <- 12
  TempK <- Temp +273.15
  #Pressure = 1
  a <- -139.34411
  b <- 1.575701e+5
  c <- 6.642308e+7
  d <- 1.243800e+10
  e <- 8.621949e+11
  DOo <- exp(a + (b/TempK) - (c/TempK^2) + (d/TempK^3) - (e/TempK^4))
  #Salinity <- 28.9
  f <- 0.017674
  g <- 10.754
  h <- 2140.7
  Fs <- exp(-Salinity * (f - g/TempK + h/TempK^2))
  #Pressure <- 2
  i <- 11.8571
  j <- 3840.7
  k <- 216961
  u <- exp(i - j/TempK - k/TempK^2)
  l <- 0.000975
  m <- 1.43e-5
  n <- 6.436e-8
  theta <- l - m*Temp + n*Temp^2
  Fp <- ((Pressure - u)*(1-theta*Pressure))/((1-u)*(1-theta))
  totalDO <- Fp * DOo * Fs
  return(totalDO)
}

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



#run saturation calcs on MasterSheetR
#satDO
MasterSheetR$solubility <- saturationfun(MasterSheetR$Temp, MasterSheetR$Salinity, MasterSheetR$patm/1000) 
MasterSheetR$solubilityumol  <- solubility*31.2627 #that number is just the conversion factor from mg to umol for O2
#View(MasterSheetR)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



#now make percent saturation column
MasterSheetR$Value <- as.numeric(MasterSheetR$Value) #warning: NAs introduced by coercion
MasterSheetR$percentsat <- (MasterSheetR$Value / MasterSheetR$solubilityumol)*100 
MasterSheetR <- na.omit(MasterSheetR) #get rid of rows that have NA values(just my fault for messing up data collection)
#View(MasterSheetR)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```



```{r}

#*********************************
## 6.) Analysis, Respirometry - Distribution Plot  
#*********************************

#plot for distribution of blanksizecorrslope as box an whisker
mode(dtotal3$Temp)
#View(dtotal3)
babymaster <- data.frame(MasterSheetR$KrillID, MasterSheetR$Temp)
babymaster <- babymaster[!duplicated(babymaster[,c("MasterSheetR.KrillID", "MasterSheetR.Temp")]),]
babymaster$KrillID <- babymaster$MasterSheetR.KrillID
#View(babymaster)
dtotal3 <- merge(x=dtotal3, y=babymaster, by = "KrillID")
dtotal3$Temp <- dtotal3$MasterSheetR.Temp
#mode(dtotal3$KrillID)
#str(dtotal3)
dtotal4 <- subset(dtotal3, Treatment != "Blank")
dtotal4$Temperature <- as.factor(dtotal4$MasterSheetR.Temp)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



#fix trials where i had the presens set to wrong temp
dtotal4$Temperature[dtotal4$TrialID == "16JUN16_03"] <- 16
dtotal4$Temperature[dtotal4$TrialID == "13JUL16_02"] <- 16
dtotal4$Temperature[dtotal4$TrialID == "19JUN16_03"] <- 12
View(dtotal4)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



###make any changes to data = subset in any ways that you need to (take out trials that you messed up etc)
dtotal4 <- subset(dtotal4, Size > 2.5)
#dtotal4 <- subset(dtotal4, slope < 0) #can i do this?
dtotal4 <- subset(dtotal4, TrialID != c("19JUN16_01"))
dtotal4 <- subset(dtotal4, TrialID != c("22JUN16_03"))
#dtotal4 <- subset(dtotal4, TrialID != c("13JUL16_06"))
#dtotal4 <- subset(dtotal4, TrialID != c("23JUL16_01"))
dtotal4 <- subset(dtotal4, MasterSheetR.KrillID != "13JUL16_06_9") #took off wrong crab??
dtotal4 <- subset(dtotal4, MasterSheetR.KrillID != "07JUL16_04_1") #died in resp
View(dtotal4)
#fix respiration rates so they're how much oxygen USED instead of how much LEFT
dtotal4$blanksizecorrslope <- dtotal4$blanksizecorrslope * (-1)
summary(dtotal4$blanksizecorrslope)
dtotal4$blankcorrslope <- dtotal4$blankcorrslope * (-1)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
```




```{r}
summaryForErrorBarsBSCS <- summarySE(subset(dtotal4, blanksizecorrslope > 0), measurevar="blanksizecorrslope", 
                                 groupvars=c("Treatment", "Temperature"), na.rm = TRUE)
View(summaryForErrorBarsBSCS)

summaryForErrorBarsBCS <- summarySE(subset(dtotal4, blankcorrslope > 0), measurevar="blankcorrslope", 
                                     groupvars=c( "Temperature"), na.rm = TRUE)
View(summaryForErrorBarsBCS)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



#mean O2 consumption per crab at 12C
# nmol/min/megalopae
(oxyPerCrab12C <- mean(subset(dtotal4, Temperature == 12 & blankcorrslope > 0)$blankcorrslope))

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```



```{r}
#PLOT YAYYY
# blank corrected; remove resp rate < 0
ggplot(subset(dtotal4, blanksizecorrslope > 0), aes(Treatment, blanksizecorrslope)) + 
 # geom_boxplot(aes(colour = Temperature), lwd=1, position = position_dodge(.8)) +  #to split by treatment AND temp
  geom_jitter(aes(colour = Temperature), position = position_jitterdodge(), alpha = 0.5) +
  geom_errorbar(data = summaryForErrorBarsBSCS, aes(x = Treatment, colour = Temperature,
                                                ymin = blanksizecorrslope - se, ymax = blanksizecorrslope + se),
                position = position_dodge(0.8)) +
  geom_point(data = summaryForErrorBarsBSCS, aes(x = Treatment, y = blanksizecorrslope, 
                                             colour = Temperature), position = position_dodge(0.8), size = 5) +
  labs( x = "Treatment", y = "Oxygen Consumption Rate\n(nmol/minute/mm of carapace length)") +
  theme_bw(base_size = 16) +
  guides(colour = guide_legend(override.aes = list(size=1))) +
  #ylim(c(0,1.1)) + 
  scale_x_discrete(labels = c("High pH\nHigh DO", "High pH\nLow DO", "Low pH\nHigh DO", "Low pH\nLow DO")) + 
  scale_color_manual(values = c("blue", "red"), name= "Temperature",
                     breaks = c("12", "16"),
                     labels = c(expression("12"*~degree*C), expression("16"*~degree*C)))


str(sizeslopesub)
#size versus blank corrected respiration rate plot, separated by temperature
sizeslopesub <- subset(dtotal4, Size != 0)
#sizeslopesub <- subset(sizeslopesub, Temp == 12)#change to 16 to look at the graph for 16degreesC trials
ggplot(subset(dtotal4, blanksizecorrslope > 0) , aes(x=Size, y=blanksizecorrslope)) +
  geom_point(aes(colour = factor(Temp))) +
  geom_smooth(data = subset(dtotal4, Temp == 12 & blanksizecorrslope > 0), method = lm, se = FALSE, aes(Size, blanksizecorrslope), colour = "blue") +
  geom_smooth(data = subset(dtotal4, Temp == 16 & blanksizecorrslope > 0),method = lm, se = FALSE, aes(Size, blanksizecorrslope), colour = "red") +
  labs(x = "Carapace length\n(mm)", y= "Oxygen Consumption Rate\n(nmol/minute/mm of carapace length)") +
  theme_bw(base_size = 16) +
  scale_color_manual(values = c("blue", "red"))
  

summary(lmList(Size ~ blankcorrslope|Temp, sizeslopesub))$r.squared
summary(lmList(Size ~ blankcorrslope|Temp, sizeslopesub))$adj.r.squared

##################################
#STATISTICAL ANALYSIS

#make a table comparing medians of each treatment by temp
x <- as.matrix(summaryBy(blanksizecorrslope ~ Treatment + Temp, data = dtotal4, FUN = median))
x <- as.list(x[,3])
x <- matrix(x, nrow = 2, ncol = 4)
colnames(x) <- c("HH", "HL", "LH", "LL")
row.names(x) <- c("12C", "16C")
View(x)

#ANOVA
tapply(dtotal4$blanksizecorrslope, dtotal4$Temp, median)
tapply(dtotal4$blanksizecorrslope, dtotal4$Treatment, median)
int <- aov(data = dtotal4, blanksizecorrslope ~ Temp*Treatment)
summary(int) #Pr(>F) column, temp:treatment row = p-value. if it's big we don't have to worry about interaction?

addint <- aov(data = dtotal4, blanksizecorrslope ~ Temp + Treatment)
summary(addint) #p-value for temp is really small??? (1.91e-11)
#omnibus test (F test) to look at main effects and interactions


ano <- anova(lm(blanksizecorrslope ~ Treatment * Temp, subset(dtotal4, blanksizecorrslope > 0)))
print (ano)
summary(lm(blanksizecorrslope ~ Treatment * Temp, dtotal4))

pairwise.t.test(dtotal4$blanksizecorrslope, dtotal4$Treatment, p.adj = "none")
pairwise.t.test(dtotal4$blanksizecorrslope, dtotal4$Temp, p.adj = "none")

#Tukey post hoc test
TukeyHSD(aov(data = dtotal4, blanksizecorrslope ~ Treatment), conf.level = 0.95)
#TukeyHSD(aov(data = dtotal4, blanksizecorrslope ~ Temp), conf.level = 0.95) #doesnt work


#what am I doing here?

```







```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT