
---
title: "Respirometry Trails for Summer Krill 2019"
output:
 html_document:
    df_print: paged
    code_folding: hide
    toc: TRUE
    toc_depth: 4
    toc_float: true
    theme: journal
    highlight: zenburn
    smart: false

---


Hello World

Author: OA Lab, NWFSC
Title: Respirometry Trails for Summer Krill 2019- Trying to Adapt to make the Package ‘FishResp’ Package work
Date: December 2020


# Version Check
```{r 0.1 Version Check , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
## Version Check
#********************************* 
R.version

```


# Libraries
```{r 0.0 Libraries , echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
#*********************************
##Libraries
#********************************* 
library(stringr)
library(tidyverse)
library(plyr)
library(nlme)
library(tidyr)
library(purrr)
library(wql)
library(lubridate)
library(arsenal)
library(compareDF)
library(FishResp)
#for graphing
library(ggplot2)
library(stringr)
library(nlme)
library(RColorBrewer)
#statistical analysis
library(gdata)
library(rsq)
library(doBy)
#Rnotebooks 
library(gridExtra)
library(kableExtra)

```


 
# 1.) Setting Working Directory
```{r 1.) Setting Working Directory }
#*********************************
## 1.) Setting Working Directory
#*********************************

#set working directory to the correct folder
setwd("/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES")
```



# 2.) Creating the Dataframe
```{r 2.) Creating the Dataframe }

#*********************************
## 2.) Creating the intial Dataframe, dRESP
#*********************************

## Method 1 - 1 file for the four trials
#get all the files in the defined working directory that are in csv format  
dRESP <- read.csv(file = "KRILL_Resp_alltrials.csv", stringsAsFactors = FALSE)
dim(dRESP)

#write.csv(dRESP, file = "2020.11.30_presenseSENSORONLY.alltrials.data.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# dRESPanimal represents just the animal, vial, MOATs, etc.  
dRESPanimal <- read.csv(file = "RespirometryTrials_all.Animal.Info.csv") 
dim(dRESPanimal)

#write.csv(dRESPanimal, file = "2020.11.30_krillanimaldata.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


#dRESPmsr represents the measurements made by the presense optical device for Dissolved Oxygen 
dRESPmsr <- merge(dRESP, dRESPanimal, by="SensorName")

#write.csv(dRESPmsr, file = "2020.12.01_respirometrymeasurements.csv", row.names = FALSE)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


# dRESP$MOATS <- factor(dRESP$MOATS)
# Checking the names of the different levels
# levels(dRESP$MOATS)


# dRESPmsr <- dRESPmsr %>% filter(!MOATS %in% c("3", "4", "5", "11")) %>%
#   filter(Treatment %in% c("CUR", "CHG", "TMP")) 
# 
# 
# dRESPmsr <- dRESPmsr %>% filter(!MOATS %in% c("3", "4", "5", "11")) %>%
#   filter(Treatment %in% c("CUR", "CHG", "TMP", "n/a")) 


```




# 3.) Creating dateTime objects 
```{r 3.) Creating dateTime objects }

#*********************************
## 3.) Creating dateTime objects  
#*********************************

dRESPmsr$dateTime <- ""
dRESPmsr$dateTime <- as.POSIXct(paste(dRESPmsr$Date,
                                      dRESPmsr$Time), "%d-%B-%y %H:%M:%S", tz="UTC")

# QA check
dim(dRESPmsr)

dRESPmsr$Time <- as.POSIXct(dRESPmsr$dateTime, format="%H:%M:%S")


```



# 4.) Cleaning up observations
```{r 4.) Cleaning up observations }
#*********************************
## 4.) Cleaning up observations  
#********************************

#Removing items with faulty sensor names
dRESPmsr <- subset(dRESPmsr, SensorName != "")

dRESPmsr$SensorName <- str_trim(dRESPmsr$SensorName, side = c("both"))
dRESPmsr$SensorName <- factor(dRESPmsr$SensorName)
dim(dRESPmsr)

dRESPmsr <- subset(dRESPmsr, Value != "---")

# Confirming proper number of krill 
# 76, 4x19 propoer number of animals under observation 
unique(dRESPmsr$SensorName)
UniqueSensorNames <- levels(dRESPmsr$SensorName)
write.table(UniqueSensorNames, file = "2020.11.30DRESPmsr_UniqueSensorNames.csv")
kable(UniqueSensorNames)

```



#5.) Creating Trial ID & Krill ID
```{r 5.) Creating Trial ID & Krill ID}
#*********************************
## 5.) Creating a Krill ID with Trial in name    
#*********************************

## First Trial began at 2019-10-28 14:25:01
## First Trial ended at 2019-10-28 16:37:29

## Second Trial began at 2019-10-28 18:55:21
## Second Trial ended at 2019-10-28 21:16:45

## Third Trial began at 2019-10-29 14:06:21
## Third Trial ended at 2019-10-29 16:18:36

## Fourth Trial began at 2019-10-29 17:20:21
## Fourth Trial ended at 2019-10-29 19:32:01


dRESPmsr$TrialID <- ""
dRESPmsr <- dRESPmsr %>% mutate(TrialID=case_when(
  
## First Trial began at 2019-10-28 14:25:01
## First Trial ended at 2019-10-28 16:37:29
  
  ((Time >= as.POSIXct("2019-10-28 14:25:00", tz = "UTC")) 
   & (Time < as.POSIXct("2019-10-28 16:37:30", tz = "UTC"))) ~ "Trial01",

  
## Second Trial began at 2019-10-28 18:55:21
## Second Trial ended at 2019-10-28 21:16:45  
  
  ((Time >= as.POSIXct("2019-10-28 18:55:20", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-28 21:16:50", tz = "UTC"))) ~ "Trial02",


## Third Trial began at 2019-10-29 14:06:21
## Third Trial ended at 2019-10-29 16:18:36


  ((Time >= as.POSIXct("2019-10-29 14:06:18", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-29 16:18:40", tz = "UTC"))) ~ "Trial03",

## Fourth Trial began at 2019-10-29 17:20:21
## Fourth Trial ended at 2019-10-29 19:32:01

  
  ((Time >= as.POSIXct("2019-10-29 17:20:18", tz = "UTC")) 
   & (Time <= as.POSIXct("2019-10-29 19:40:01", tz = "UTC"))) ~ "Trial04",

  TRUE ~"other"
)) 

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

## new value 
## dRESPmsr$KrillID

dRESPmsr$KrillID <- ""

dRESPmsr$KrillID <- paste(dRESPmsr$TrialID, "_", dRESPmsr$SensorName, sep="")
#View(dRESPmsr)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |


```



# 6.) DO Corrections
```{r 6.) DO trial 3 correction applied to all rounds}
#*********************************
## 6.) DO trial 3 correction applied to all rounds   
#*********************************

# New values to correct the DO values for the temperature in Trial 3 in the dataframe dRESPmsr

dRESPmsr$percentDOassumpt <- ""
dRESPmsr$assumedSatDOmg <- ""
dRESPmsr$percentDO <- ""
dRESPmsr$obseveredSatDOmg <- ""
dRESPmsr$actualDOmg <- ""

dRESPmsr$percentDOassumpt <- as.numeric(dRESPmsr$percentDOassumpt)
dRESPmsr$assumedSatDOmg <- as.numeric(dRESPmsr$assumedSatDOmg)
dRESPmsr$percentDO <- as.numeric(dRESPmsr$percentDO)
dRESPmsr$obseveredSatDOmg <- as.numeric(dRESPmsr$obseveredSatDOmg)
dRESPmsr$actualDOmg <- as.numeric(dRESPmsr$actualDOmg)
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Correct Temperature
dRESPmsr$CorTemp <- 11

#Salinity Constant
dRESPmsr$SalinityConstant <- 30.3
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# Numeric Corrections to DO value
dRESPmsr$Value <- as.numeric(dRESPmsr$Value)

dRESPmsr$assumedSatDOmg <- oxySol(dRESPmsr$CorTemp, 
                                  dRESPmsr$SalinityConstant)

dRESPmsr$percentDOassumpt <- dRESPmsr$Value / dRESPmsr$assumedSatDOmg

dRESPmsr$obseveredSatDOmg <- oxySol(dRESPmsr$CorTemp, dRESPmsr$SalinityConstant)

dRESPmsr$percentDO <- dRESPmsr$Value / dRESPmsr$assumedSatDOmg

dRESPmsr$actualDOmg <- dRESPmsr$percentDO * dRESPmsr$obseveredSatDOmg


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
```




# 6.a) DO table & DO correction Plot Check
```{r 6.a) DO table & DO correction Plot Check  }
#*********************************
## 6.a) DO table & DO correction Plot Check  
#*********************************

# write.table(dRESPmsr, file = "2020.11.06.dRESPmeasurements", sep=";", 
#             row.names = TRUE)
# 
# dRESPmsr <-subset(dRESPmsr, actualDOmg != "---")
# dRESPmsr$Time <- as.POSIXct(dRESPmsr$Time, format="%H:%M:%S")
ggplot(dRESPmsr, aes(x = Time, y = actualDOmg, colour = SensorName)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  facet_wrap(~TrialID) +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  theme_bw()

```


# 7.) Plotting Percent DO by Trial (80%)

## 7.1a Placeholder for load map graphic
![Trial01 Loading Map](/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES/Trial01of2(2019.10.28)respirometry.png)


## 7.1) PLotting Percent DO filtering Trial 1
```{r 7.1) PLotting Percent DO filtering Trial 1}

Trial1percentDO <- filter(dRESPmsr, TrialID == "Trial01")


levels(Trial1percentDO$Treatment)

ggplot(Trial1percentDO, aes(x = Time, y = percentDO, colour = SensorName)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  ggtitle("Trial01 Percent DO") +
  facet_wrap(~ Treatment) + 
  geom_hline(yintercept = c(.8), colour = "red") +
  theme_bw()


```


## 7.2a Placeholder for load map graphic
![Trial02 Loading Map](/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES/Trial02of2(2019.10.28)respirometry.png)

## 7.2) PLotting Percent DO filtering Trial 2
```{r 7.2) PLotting Percent DO filtering Trial 2}

Trial2percentDO <- filter(dRESPmsr, TrialID == "Trial02")


ggplot(Trial2percentDO, aes(x = Time, y = percentDO, colour = SensorName)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  ggtitle("Trial02 Percent DO") +
  facet_wrap(~ Treatment) + 
   geom_hline(yintercept = c(.8), colour = "red") +
  theme_bw()


```


## 7.3a Placeholder for load map graphic
![Trial03 Loading Map](/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES/Trial01of2(2019.10.29)respirometry.png)


## 7.3) PLotting Percent DO filtering Trial 3
```{r 7.3) PLotting Percent DO filtering Trial 3}

Trial3percentDO <- filter(dRESPmsr, TrialID == "Trial03")


ggplot(Trial3percentDO, aes(x = Time, y = percentDO, colour = SensorName)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  ggtitle("Trial03 Percent DO") +
  facet_wrap(~ Treatment) + 
   geom_hline(yintercept = c(.8), colour = "red") +
  theme_bw()


```


## 7.4a Placeholder for load map graphic
![Trial04 Loading Map](/Users/katherinerovinski/GIT/NWFSC.MUK_KRL2019respirometrySLOPES/Trial02of2(2019.10.29)respirometry.png)

## 7.4) PLotting Percent DO filtering Trial 4
```{r 7.4) PLotting Percent DO filtering Trial 4}

Trial4percentDO <- filter(dRESPmsr, TrialID == "Trial04")


ggplot(Trial4percentDO, aes(x = Time, y = percentDO, colour = SensorName)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  ggtitle("Trial04 Percent DO") +
  facet_wrap(~ Treatment) + 
   geom_hline(yintercept = c(.8), colour = "red") +
  theme_bw()


```



# 8.) Analysis, Respirometry - Creating the Slope Function 
```{r 8.) Analysis, Respirometry - Creating the Slope Function}
#*********************************
## 8.) Analysis, Respirometry - Creating the Slope Function  
#*********************************  

vialVol <- 28.06 #ml

oxygen <- vialVol * dRESPmsr$actualDOmg   

dRESPmsr$oxygen <- oxygen


#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
#nmol/vial; conversion for L to ml and umol to nmol cancels
#slope funcion of 2 vectors
slope <- function(y,x){
  return(lm(y~x, na.action = na.omit)$coefficients[2])
}
  
#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
dRESPmsr$delta_t <- as.numeric(dRESPmsr$delta_t)

cSlopes <- by(dRESPmsr, dRESPmsr$KrillID, function(x){ slope(x$oxygen, x$delta_t)})

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#creating a data frame instead of a list 
ds <- as.data.frame(sapply(cSlopes, I))
#having row names be a variable in a column to be able to pull it out for later merging 
ds$TrialID<- row.names(ds)



```



# 9.) Merging ds and dRESPmsr 
```{r 9.) Merging ds and dRESPmsr}
#add column to dslopes thats KrillID
#View(dref)
ds$KrillID <- row.names(ds)
#View(dslopes)
dtotal <- merge(dRESPmsr, ds, by = "KrillID")
#View(dtotal)

```



# 10.) Krill ID as a factor & Grouping by Krill ID
```{r 10.) Krill ID as a factor & Grouping by Krill ID}
dtotal$KrillID <- factor(dtotal$KrillID)
nlevels(dtotal$KrillID)


```



# 11.) Analysis, Respirometry - Creating Slope Functions & Linear Models  
```{r 11.) Analysis, Respirometry - Creating Slope Functions & Linear Models  }
#*********************************
## 11.1) Creating the ds dataframe
#*********************************
# #get slopes and r^2 values from dtotal 

dSlopes <- data.frame(KrillID = levels(dtotal$KrillID))
# dSlopes$slope <- NA
# dSlopes$rsq <- NA

for(i in 1:length(dSlopes$KrillID)){
   m <- lm(oxygen ~ delta_t,
                         dtotal[dtotal$KrillID == dSlopes$KrillID[i],],
                         na.action=na.omit)
  dSlopes$slope[i] <- m$coefficients[2]
  dSlopes$rsq[i] <- summary(m)$r.squared
}

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

krillslopes <- merge(dtotal, dSlopes, by="KrillID")

dSlopes$SensorName <- ""

dSlopes <- dSlopes %>% group_by(KrillID)
dRESPanimal <- dRESPanimal %>% group_by(SensorName)

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

dSlopes$KrillID <- as.character(dSlopes$KrillID)
dSlopes$SensorName <- dRESPanimal$SensorName
dSlopes$TrialID <- dRESPanimal$TrialID
dSlopes$MOATS <- dRESPanimal$MOATS
dSlopes$Treatment<- dRESPanimal$Treatment
dSlopes$LoadingLocation<- dRESPanimal$LoadingLocation
dSlopes$VialNum<- dRESPanimal$GlassVialNumber
dSlopes$TelsonLength<- dRESPanimal$TelsonLength..mm.
dSlopes$WetWeight<- dRESPanimal$Size

# #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

```


# 12.) Analysis, Respirometry - Correcting the Slope for Blanks
```{r 12.) Analysis, Respirometry - Correcting the Slope for Blanks}

#*********************************
## 12.) Analysis, Respirometry - Correcting the Slope for Blanks 
#*********************************

#blank corrected slope and blank-size corrected slope
## need to correct all slopes with the blanks' slope
## this is the background respiration of whatever phtyos and instrument drift
## create a mean blank slope per trial
## merge with the master(krill slopes) and "correct" all slopes against mean value (per trial)
# x is equal to the blank vials  

# #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

# Creating four seperate means from the blank vials per trial
x <- subset(dSlopes, dSlopes$MOATS == "blank")

xtrial1 <- subset(x, x$TrialID == "Trial01")
xtrial2 <- subset(x, x$TrialID == "Trial02")
xtrial3 <- subset(x, x$TrialID == "Trial03")
xtrial4 <- subset(x, x$TrialID == "Trial04")

blankmeanslope1 <- mean(xtrial1$slope)
blankmeanslope2 <- mean(xtrial2$slope)
blankmeanslope3 <- mean(xtrial3$slope)
blankmeanslope4 <- mean(xtrial4$slope)

# #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |

#Creating new corrected varibles for slopes adjusted for blank vials and size of animal
dSlopes$CorrSlope <- ""
dSlopes$CorrSlope <- as.numeric(dSlopes$CorrSlope)
dSlopes$slope <- as.numeric(dSlopes$slope)

# #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
# Conditonal Statement directing certain means to their respective trials
dSlopes <- dSlopes %>% mutate(CorrSlope=case_when(
    (dSlopes$MOATS == "blank" ~ dSlopes$slope),
    (dSlopes$TrialID == "Trial01" ~ dSlopes$slope-blankmeanslope1),
    (dSlopes$TrialID == "Trial02" ~ dSlopes$slope-blankmeanslope2),
    (dSlopes$TrialID == "Trial03" ~ dSlopes$slope-blankmeanslope3),
    (dSlopes$TrialID == "Trial04" ~ dSlopes$slope-blankmeanslope4),
    TRUE ~ as.numeric(0)
))
# #|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |
# Correcting for the size of the animal 
dSlopes$WetWeight <- as.numeric(dSlopes$WetWeight)
dSlopes$WetWeightSlope <- dSlopes$CorrSlope/dSlopes$WetWeight

#|- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - |



```



# 13.x Messing with period of observation delta_t aggregated
```{r 13.x Messing with period of observation delta_t aggregated}

Sumdelta_t <- aggregate(dRESPmsr$delta_t, by=list(Category=dRESPmsr$KrillID), FUN=(sum))
Sumdelta_t$KrillID <- Sumdelta_t$Category
Sumdelta_t$x <- as.numeric(Sumdelta_t$x)

Sumdelta_t$Interval.mins <- (Sumdelta_t$x/60)

dSlopes <- merge(dSlopes, Sumdelta_t , by="KrillID")


dRESPmsr <- dRESPmsr %>% group_by(Time)
# Subset by KrillID
# Run head() & tail() on each subset

smallFrame <- dtotal %>%
    group_by(KrillID) %>%
    dplyr::mutate(
        first = dplyr::first(Time),
        last = dplyr::last(Time)
    )

SRTSTPslope <- dtotal %>%
group_by(KrillID) %>%
slice(c(1, n())) %>%
ungroup()




```



# 14.) Plots I guess... terrible
```{r 14.0) plots I guess  Trial 1}

dTOTslopePLOTs <- merge(dtotal, dSlopes, by="KrillID")


Trial1correctedslopes <- filter(dTOTslopePLOTs, TrialID == "Trial01")

ggplot(Trial1correctedslopes, aes(x=Time, y=CorrSlope)) + 
  geom_point(aes(colour= MOATS.x, point=)) + 
  ggtitle("All MOATs, All Treatments Corrected Slopes") 


ggplot(Trial1correctedslopes, aes(x =Time, y = CorrSlope, colour = KrillID)) +
  geom_point(size = 1) +
  geom_smooth(method = "lm") +
  #scale_y_continuous(breaks=seq(250,950,by=50))   +
  ggtitle("Trial01 corrected slopes") +
  facet_wrap(~ Treatment.y) +
   # geom_hline(yintercept = c(.8), colour = "red") +
  theme_bw()


```


# 14.x What if I plotted some boxplots
```{r}


dSlopes1 <- dSlopes %>% filter(CorrSlope<=10) # %>%
  
  # filter(Treatment %in% c("current", "allchange", "hightemperature"))


dSlopes2 <- dSlopes %>% filter(CorrSlope<=10) %>%
            filter(Treatment %in% c("CUR", "CHG", "TMP"))


ggplot(dSlopes2, aes(Treatment, CorrSlope)) +
            geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = dSlopes2, aes(x=Treatment, y=CorrSlope), size=1, color = "purple") + 
            facet_wrap(~TrialID) +
            ggtitle("All Treatments, All Trials, Corrected Slopes") +
            theme_bw() 




```

# 14.xx More terrible plots

```{r}

ggplot(dSlopes2, aes(Treatment, CorrSlope)) +
            # geom_jitter(color = "grey") +
            geom_boxplot(notch = TRUE, outlier.shape = NA, colour = "green") +
            geom_point(data = dSlopes2, aes(x=Treatment, y=CorrSlope), size=1, color = "purple") + 
            ggtitle("All Treatments, All Trials, Corrected Slopes") +
            theme_bw() 

```







```{r}
#**************E*N*D*************# 
#*********************************
## END OF SCRIPT | END OF DOCUMENT 
#*********************************
```


## END OF SCRIPT | END OF DOCUMENT


